Extract team means and SDs

### 2023-01-18 RR_manuscript/supplementary_materials.Rmd

---
title: "Supplementary materials"
output: pdf_document
date: "`r Sys.Date()`"
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = here::here())
library("dplyr")
library("ggplot2")
library("tidyr")
library("readr")
library("googlesheets4")
library("glue")
library("here")
library("fs")
library("forcats")
library("purrr")
library("stringr")
library("kableExtra")
```

@@

# Create DF of all members with leader names
team_leaders <- readr::read_csv(
  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
  select(ResponseId, Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  mutate(leader = Q6, 
         leader = case_when(
           Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali H. Al-Hoorie", 
           Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia M Brown", 
           Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
           Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
           Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dušan Nikolić", 
           Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
           Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
           Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perry", 
           Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
           Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
           Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vince Hughes", 
           Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
           TRUE ~ leader
         )) %>% 
  select(ResponseId, leader)

@@

# Vector of teams with submitted analyses (for subsetting)
submitted_animals <- readRDS(here("./data/analyses/msa_models.rds")) %>% 
  pull(animal) %>% 
  unique
teams_used_in_analysis <- teams %>% 
  filter(animal %in% submitted_animals) %>% 
  pull(coordinator)

>>>>

---
title: |
  Multidimensional signals and analytic flexibility:  
  Estimating degrees of freedom in human speech analyses
subtitle: "Supplementary materials"
author: |
  Initiating authors:  
  Stefano Coretta, Joseph V. Casillas, and Timo Roettger
output: pdf_document
date: "`r Sys.Date()`"
header-includes: 
  - \pagenumbering{gobble}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = here::here())
library("dplyr")
library("ggplot2")
library("tidyr")
library("readr")
library("googlesheets4")
library("glue")
library("here")
library("fs")
library("forcats")
library("purrr")
library("stringr")
library("kableExtra")
```

```{r}
#| label: sankey-plot
#| fig.cap: "Sankey plot illustrating workflow choices from analyst teams."
#| out.width: "100%"
knitr::include_graphics(path = "./figs/flow_outcome.png")
```

@@

# Create DF of all members with leader names
team_leaders <- readr::read_csv("./data/questionnaires/msa_intake_form.csv") %>%
  select(ResponseId, Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  mutate(leader = Q6, 
         leader = case_when(
           Q6 %in% c("Ali A-Hoorie", "Ali Al-Hoorie", "Ali H. Al-Hoorie") ~ "Ali H. Al-Hoorie", 
           Q6 %in% c("Alicea Megan Brown", "Alicia Brown") ~ "Alicia M Brown", 
           Q6 %in% c("Dr Rory Turnbull", "Rory Turnbull") ~ "Rory Turnbull", 
           Q6 %in% c("Dr. Reenu Punnoose", "Reenu Punnoose") ~ "Reenu Punnoose", 
           Q6 %in% c("Dušan Nickolić", "Dušan Nikolić", "Dusan Nikolic", "Dusan Nikolic (dusan.nikolic1@ucalgary.ca)") ~ "Dušan Nikolić", 
           Q6 %in% c("Michael Gradoville (Arizona State Univ.)", "Michael Gradoville") ~ "Michael Gradoville", 
           Q6 %in% c("Nicole Rodriquez", "Nicole Rodriguez") ~ "Nicole Rodriguez", 
           Q6 %in% c("Scott James Perru", "Scott Perry") ~ "Scott James Perry", 
           Q6 %in% c("Tiphaine Caudrelier", "Tiphaine Cordelier") ~ "Tiphaine Caudrelier", 
           Q6 %in% c("University of Birmingham team under the team coordinator Zlatomira IIchovska", "Zlatomira IIchovska", "Zlatomira Ilchovska") ~ "Zlatomira Ilchovska", 
           Q6 %in% c("Vincent Hughes", "Vince Hughes") ~ "Vince Hughes", 
           Q6 == "Joey Stanley" ~ "Joseph A. Stanley",
           TRUE ~ leader
         )) %>% 
  select(ResponseId, leader)

@@

# Vector of teams with submitted analyses (for subsetting)
submitted_animals <- readRDS("./data/analyses/msa_models.rds") %>% 
  pull(animal) %>% 
  unique
teams_used_in_analysis <- teams %>% 
  filter(animal %in% submitted_animals) %>% 
  pull(coordinator)

### 2023-01-18 scripts/r/07_team-sds.Rmd

1. Get a list of the subset of teams that need to be downloaded (Max = 30 because the final model only includes 30 teams). 
2. Download the OSF components of the aforementioned subset of teams.
3. Use the code found in `04_refit` (i.e., `refit_jvc.Rmd`, `refit_sc.Rmd` and `refit_tr.Rmd`) to get the final data frames used in the original analyses. 
4. Calculate mean/SD of the raw DVs (only f0, duration, and intensity). 
5. Store means/SDs in a separate .csv file in `data/analyses`.

@@

Of the 30 teams included in the meta-analysis, `r length(final_team_names)` included either F0, duration or intensity in the analyses. 
Next, we download the OSF components of those `r length(final_team_names)` teams.

@@

@@

In order to get the data frame from each teams analysis, we will recycle code from `04_refit` (i.e., `refit_jvc.Rmd`, `refit_sc.Rmd` and `refit_tr.Rmd`). 
We can pull in specific lines of code with the `source_part` function. 
If we can't source the lines directly without touching the refit_xx.Rmd files (because *some* people refuse to use `here`), then we will have to copy/paste code to this file and adjusts the paths like heathens.

@@

```{r}
#| label: anomalocaris_ornata
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 131, 
  end = 181
  )

@@

```{r}
#| label: arapaima_modularis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 392, 
  end = 441
  )

@@

```{r}
#| label: clione_dorsalis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1379, 
  end = 1395
  )

@@

```{r}
#| label: comanthina_maculatus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 478, 
  end = 489
  )

@@

```{r}
#| label: cromileptes_saxatilis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 527, 
  end = 530
  )

@@

```{r}
#| label: gnathosaurus_canadensis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 602, 
  end = 606
  )

@@

```{r}
#| label: gymnothorax_spinulosus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 644, 
  end = 662
  )

@@

```{r}
#| label: haematopus_fossor
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 714, 
  end = 845
  )

@@

```{r}
#| label: lasionycteris_altavela
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 955, 
  end = 962
  )

@@

```{r}
#| label: naso_cassivellaunos
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1054, 
  end = 1067
  )

@@

```{r}
#| label: psittacula_scabriculus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1295, 
  end = 1327
  )

@@

```{r}
#| label: trapezia_cantonensis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1206, 
  end = 1214
  )

@@

# Super long because somebody refuses to use `here` and I don't want to modify `refit_sc.Rmd`
# The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
trial_dat <- list.files(path = here("data", "osf", "production", "trial-lists"),
                       pattern = "*.csv",
                       full.names = TRUE) %>%
  lapply(read_csv) %>%                              
  bind_rows

@@

@@

```{r}
#| label: chelonia_brummeri
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1532, 
  end = 1600
  )

@@

```{r}
#| label: dunkleosteus_inscriptus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1309, 
  end = 1420
  )

@@

@@

```{r}
#| label: procambarus_mahogoni
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1742, 
  end = 1745
  )

@@

@@

```{r}
#| label: trachyphyllia_lappa
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 49, 
  end = 134
  )

@@

# Comnine tibbles 
msa_mean_sd <- bind_rows(
  anomalocaris_ornata_df, 
  anthracoceros_coronata_df, 
  arapaima_modularis_df, 
  clione_dorsalis_df, 
  comanthina_maculatus_df, 
  cromileptes_saxatilis_df, 
  gnathosaurus_canadensis_df, 
  gymnothorax_spinulosus_df, 
  haematopus_fossor_df, 
  lasionycteris_altavela_df, 
  naso_cassivellaunos_df, 
  psittacula_scabriculus_df, 
  trapezia_cantonensis_df, 
  dermatolepis_aculeatus_df, 
  eriphia_laterispinis_df, 
  hoplostethus_macrosteus_df, 
  neosilurus_omanensis_df, 
  nestor_idahoensis_df, 
  paralichthys_undulatus_df, 
  petauroides_fistulator_df, 
  saron_pictus_df, 
  trachurus_riukiuensis_df, 
  varanus_eulophotes_df, 
  alosa_atun_df, 
  chelonia_brummeri_df, 
  dunkleosteus_inscriptus_df, 
  pervagor_meeki_df, 
  procambarus_mahogoni_df, 
  trachyphyllia_lappa_df
)

>>>>

1. Get a list of the subset of teams that need to be downloaded (Max = 33 because the final model only includes 33 teams). 
2. Download the OSF components of the aforementioned subset of teams.
3. Use the code found in `04_refit` (i.e., `refit_jvc.Rmd`, `refit_sc.Rmd` and `refit_tr.Rmd`) to get the final data frames used in the original analyses. 
4. Calculate mean/SD of the raw DVs (only f0, duration, and intensity). 
5. Store means/SDs in a separate .csv file in `data/analyses`.

@@

Of the `r length(teams)` teams included in the meta-analysis, `r length(final_team_names)` included either F0, duration or intensity in the analyses. 
Next, we download the OSF components of those `r length(final_team_names)` teams.

@@

Note: Downloading from OSF can be buggy due to server limitations. 
If you have any issues getting all of the components, you can download them manually here: <https://osf.io/n3fyd/>.

@@

In order to get the data frame from each teams analysis, we will recycle code from `04_refit` (i.e., `refit_jvc.Rmd`, `refit_sc.Rmd` and `refit_tr.Rmd`). 
We can pull in specific lines of code with the `source_part` function. 
If we can't source the lines directly without touching the refit_xx.Rmd files, then we will have to copy/paste code to this file and adjusts the paths.

@@

```{r}
#| label: anomalocaris_ornata
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 131, 
  end = 183
  )

@@

```{r}
#| label: arapaima_modularis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 394, 
  end = 443
  )

@@

```{r}
#| label: clione_dorsalis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1387, 
  end = 1403
  )

@@

```{r}
#| label: comanthina_maculatus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 480, 
  end = 491
  )

@@

```{r}
#| label: cromileptes_saxatilis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 533, 
  end = 536
  )

@@

```{r}
#| label: gnathosaurus_canadensis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 608, 
  end = 612
  )

@@

```{r}
#| label: gymnothorax_spinulosus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 650, 
  end = 668
  )

@@

```{r}
#| label: haematopus_fossor
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 720, 
  end = 859
  )

@@

```{r}
#| label: lasionycteris_altavela
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 961, 
  end = 968
  )

@@

```{r}
#| label: naso_cassivellaunos
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1060, 
  end = 1073
  )

@@

```{r}
#| label: psittacula_scabriculus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1303, 
  end = 1335
  )

@@

```{r}
#| label: trapezia_cantonensis
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_jvc.Rmd"), 
  start = 1214, 
  end = 1222
  )

@@

# The following code reads in the thirty different .csv files with the trial-level data and merges them into a single dataframe
trial_dat <- list.files(path = here("data", "osf", "production", "trial-lists"),
                       pattern = "*.csv",
                       full.names = TRUE) %>%
  lapply(read_csv) %>%                              
  bind_rows

@@

### sphyrna_ellioti

```{r}
#| label: sphyrna_ellioti
#| eval: true

source_part(
  file = here("scripts", "r", "04_refit", "refit_sc.Rmd"), 
  start = 537, 
  end = 558
  )

# Means and SDs
sphyrna_ellioti_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "sphyrna_ellioti", 1, "duration",  mean(pro_df$Duration..ms.), sd(pro_df$Duration..ms.), 
  "sphyrna_ellioti", 2, "intensity", mean(pro_df$Intensity),     sd(pro_df$Intensity), 
  "sphyrna_ellioti", 3, "f0",        mean(pro_df$fo1),          sd(pro_df$fo1), 
  "sphyrna_ellioti", 4, "f0",        mean(pro_df$fo2),          sd(pro_df$fo2), 
  "sphyrna_ellioti", 5, "f0",        mean(pro_df$fo3),          sd(pro_df$fo3)
)

# Check n models == n DVs
final_teams %>% filter(animal == "sphyrna_ellioti") %>% nrow == nrow(sphyrna_ellioti_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "sphyrna_ellioti") %>% pull(outcome) == sphyrna_ellioti_df %>% pull(dv)
```

@@

```{r}
#| label: chelonia_brummeri
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1592, 
  end = 1661
  )

@@

```{r}
#| label: dunkleosteus_inscriptus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1369, 
  end = 1480
  )

@@

### procambarus_maculosus

```{r}
#| label: procambarus_maculosus
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1153, 
  end = 1288
  )

# Means and SDs
procambarus_maculosus_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "procambarus_maculosus", 1,  "f0",  mean(info$s1), sd(info$s1), 
  "procambarus_maculosus", 2,  "f0",  mean(info$s2), sd(info$s2)
)

# Check n models == n DVs
final_teams %>% filter(animal == "procambarus_maculosus") %>% nrow == nrow(procambarus_maculosus_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "procambarus_maculosus") %>% pull(outcome) == procambarus_maculosus_df %>% pull(dv)

@@

```{r}
#| label: procambarus_mahogoni
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1802, 
  end = 1812
  )

@@

### pseudopleuronectes_assasi

```{r}
#| label: pseudopleuronectes_assasi
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 1872, 
  end = 1892
  )

# Means and SDs
pseudopleuronectes_assasi_df <- tribble(
  ~"animal", ~"model_n", ~"dv", ~"mean", ~"sd", 
  "pseudopleuronectes_assasi", 1,  "duration",  mean(NF1$Duration), sd(NF1$Duration), 
  "pseudopleuronectes_assasi", 2,  "f0",        mean(NF1$MedianST), sd(NF1$MedianST), 
  "pseudopleuronectes_assasi", 3,  "intensity", mean(NF1$MedianInt), sd(NF1$MedianInt)
)

# Check n models == n DVs
final_teams %>% filter(animal == "pseudopleuronectes_assasi") %>% nrow == nrow(pseudopleuronectes_assasi_df)

# Check DVs are the same as those listen in model excel
final_teams %>% filter(animal == "pseudopleuronectes_assasi") %>% pull(outcome) == pseudopleuronectes_assasi_df %>% pull(dv)
```

@@

```{r}
#| label: trachyphyllia_lappa
#| eval: true
source_part(
  file = here("scripts", "r", "04_refit", "refit_tr.Rmd"), 
  start = 50, 
  end = 135
  )

@@

# Comnine tibbles 
msa_mean_sd <- bind_rows(
  anomalocaris_ornata_df, 
  anthracoceros_coronata_df, 
  arapaima_modularis_df, 
  clione_dorsalis_df, 
  comanthina_maculatus_df, 
  cromileptes_saxatilis_df, 
  gnathosaurus_canadensis_df, 
  gymnothorax_spinulosus_df, 
  haematopus_fossor_df, 
  lasionycteris_altavela_df, 
  naso_cassivellaunos_df, 
  psittacula_scabriculus_df, 
  trapezia_cantonensis_df, 
  dermatolepis_aculeatus_df, 
  eriphia_laterispinis_df, 
  hoplostethus_macrosteus_df, 
  neosilurus_omanensis_df, 
  nestor_idahoensis_df, 
  paralichthys_undulatus_df, 
  petauroides_fistulator_df, 
  saron_pictus_df, 
  sphyrna_ellioti_df, 
  trachurus_riukiuensis_df, 
  varanus_eulophotes_df, 
  alosa_atun_df, 
  chelonia_brummeri_df, 
  dunkleosteus_inscriptus_df, 
  pervagor_meeki_df, 
  procambarus_maculosus_df, 
  procambarus_mahogoni_df, 
  pseudopleuronectes_assasi_df,
  trachyphyllia_lappa_df
)
